---
title: "p8105_hw1_wq2161"
author: "Wanxin Qi"
date: "9/22/2021"
output: github_document
---

# Problem 1

## Part 1

Load the necessary packages.

```{r load_packages}
library(tidyverse)
```

Set up the data frame.

```{r p1_df_setup}
set.seed(12)

p1_df =
  tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_fact = factor(c("small", "large", "medium", "large", "large",
                        "medium", "small", "small", "large", "medium"))
  )

p1_df
```

## Part 2

Take the mean of each variable in the data frame.

```{r p1_mean, message = FALSE, warning = FALSE}
mean(pull(p1_df, sample))

mean(pull(p1_df, gr_than_0))

mean(pull(p1_df, vec_char))

mean(pull(p1_df, vec_fact))
```

The mean of the sample variable, **sample**, and the logical variable, **gr_than_0**, worked; the mean of the character variable, **vec_char**, and the factor variable, **vec_fact**, didn't work.

## Part 3

Apply the *as.numeric* function to the logical, character, and factor variables.

```{r p1_as_numeric, eval = FALSE}
as.numeric(pull(p1_df, gr_than_0))

as.numeric(pull(p1_df, vec_char))

as.numeric(pull(p1_df, vec_fact))
```

For the logical variable, it became FALSE = 0 and TRUE = 1, which explained the output of the mean.

For the character variable, NAs were introduced by coercion, which explained the output of the mean.

For the factor variable, numbers 1, 2, 3 were assigned to each factor. However, the mean in part 2 returned NA.

# Problem 2

## Part 1

Load the **penguins** dataset.

```{r p2_load_dataset}
data("penguins", package = "palmerpenguins")
```

`r summary(penguins)`.

The dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

## Part 2

Make a scatterplot of **flipper_length_mm** vs. **bill_length_mm**; color points using the **specious** variable; export the scatterplot to the project directory using *ggsave*.

```{r p2_scatterplot, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species) ) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

